Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
quickfixes

\begin{figure}[t]
  \centering
  \input{lattice.tikz}
  \caption{\label{fig:lattice-representation} Representation of a
    2d cell complex (here the star of a given curve) as a lattice
    map. From 65 cells (with two coordinates) on the left, we get 11
    intervals on the right.}
\end{figure}

@@

We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
the running times to compute global visibility of both \cite[Algorithm
  3]{lachaud:2022-jmiv} and our algorithm. Timings are very
similar. Our algorithm is faster for smaller maximal radii (up to 20),
while the other is slightly faster for bigger radii. We have also
measured the (discrete) average visibility distance along digitization
of smooth shapes (Fig.~\ref{fig:meanvisibility-gridstep}). It follows
a law proportionnal to $\sqrt{h}$. As shown in the next section, for
real 3d images, a maximal radius below 10 is sufficient for normal and
curvature estimation.

\begin{figure}[t]
  \centering
  \input{pointelscomptime.tikz}
  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
    time of visibility as a function of the number of pointels. We
    compare the running time of the naive breadth first visibility
    algorithm against our algorithm using intervals. We input the same
    maximal radius to both versions (10, 20, 30) and test it on 6
    different figures (goursat, torus, rcube, sphere9, leopold,
    ``D20'') with various gridsteps, ($\#$ pointels ranging from 520
    to 390235.}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \input{lattice.tikz}
  \caption{\label{fig:lattice-representation} Representation of a
    2d cell complex (here the star of a given curve) as a lattice
    map. From 63 cells (with two coordinates) on the left, we get 11
    intervals on the right.}
\end{figure}

@@

We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
the running times to compute global visibility of both~\cite[Algorithm
  3]{lachaud:2022-jmiv} and our algorithm. Timings are very
similar. Our algorithm is faster for smaller maximal radii (up to 20),
while the other is slightly faster for bigger radii. We have also
measured the (discrete) average visibility distance along digitization
of smooth shapes (Fig.~\ref{fig:meanvisibility-gridstep}). It follows
a law proportionnal to $\sqrt{h}$. As shown in the next section, for
real 3d images, a maximal radius below 10 is sufficient for normal and
curvature estimation.

\begin{figure}[t]
  \centering
  \input{pointelscomptime.tikz}
  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
    time of visibility as a function of the number of pointels. We
    compare the running time of the naive breadth first visibility
    algorithm against our algorithm using intervals. We input the same
    maximal radius to both versions (10, 20, 30) and test it on 6
    different figures (goursat, torus, rcube, sphere9, leopold,
    ``D20'') with various gridsteps, ($\#$ pointels ranging from 520
    to 390235).}
\end{figure}
